Ms 1

### 2017-06-04 ms1/ms1_display.Rmd
ms1 cohort

```{r global_options, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE,
                      error=FALSE, autodep=TRUE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace, str_detect)

@@

@@

```{r}
dat = read_tsv('tables/tbl_claims_by_abx.tsv')
totals = dat %>% group_by(year) %>% summarize(cpkp=sum(cpkp)) %>% mutate(antibiotic='all')
top_abx = dat %>%
  group_by(antibiotic) %>%
  summarize(cpkp=mean(cpkp)) %>%
  arrange(desc(cpkp)) %$%
  head(antibiotic, 10)

x = dat %>%
  select(antibiotic, year, cpkp) %>%
  filter(antibiotic %in% top_abx) %>%
  bind_rows(totals) %>%
  mutate(antibiotic=factor(antibiotic, levels=c('all', top_abx)))

x %>%
  mutate(cpkp=round(cpkp)) %>%
  spread(year, cpkp) %>%
  arrange(desc(`2011`)) %>%
  kable

x %>% ggplot(aes(x=year, y=cpkp)) +
  facet_wrap(~ antibiotic, ncol=3, scales='free_y') +
  geom_point() + geom_line() +
  theme_minimal()
```

@@

@@

```{r}
condition_names = read_tsv('../chronic-conditions/names.txt',
                           col_names=c('condition', 'condition_name'))

>>>>

```{r global_options, include=FALSE, cache=FALSE}
knitr::opts_chunk$set(fig.width=12, fig.height=8, fig.path='fig/', dev=c('pdf', 'png'),
                      echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE,
                      error=FALSE, autodep=TRUE)
import::from(knitr, kable)
import::from(lazyeval, interp)
import::from(broom, tidy)
import::from(stringr, str_replace, str_detect)
import::from(forcats, as_factor)

@@

And the same in the cohort:

```{r}
read_tsv('tables/tbl_cohort_totals.tsv') %>%
  pctize('n_bene') %>%
  select(year, n_bene, mean_age, mean_n_cc,
         pct_female, pct_white, pct_dual,
         pct_region_south, pct_region_midwest, pct_region_northeast, pct_region_west) %>%
  mutate_at(vars(starts_with('pct_')), function(x) round(x, digits=1)) %>%
  mutate(n_bene=prettyNum(n_bene, big.mark=','),
         mean_age=round(mean_age, digits=1),
         mean_n_cc=round(mean_n_cc, digits=2)) %>%
  gather('var', 'val', -year) %>% spread(year, val) %>% # transpose
  kable
```

@@

```{r}
dat = read_tsv('tables/tbl_claims_by_abx.tsv')
cohort_dat = read_tsv('tables/tbl_cohort_claims_by_abx.tsv')

top_abx = dat %>%
  group_by(antibiotic) %>%
  summarize(cpkp=mean(cpkp)) %>%
  arrange(desc(cpkp)) %$%
  head(antibiotic, 10)

top_abx_f = function(df) {
  totals = group_by(df, year) %>%
    summarize(cpkp=sum(cpkp)) %>%
    mutate(antibiotic='all')

  df %>%
    select(antibiotic, year, cpkp) %>%
    filter(antibiotic %in% top_abx) %>%
    bind_rows(totals) %>%
    mutate(antibiotic=factor(antibiotic, levels=c('all', top_abx)))
}

#top_abx_f(dat) %>%
#  mutate(cpkp=round(cpkp)) %>%
#  spread(year, cpkp) %>%
#  arrange(desc(`2011`)) %>%
#  kable

all_dat = bind_rows(
  top_abx_f(dat) %>% mutate(group='all'),
  top_abx_f(cohort_dat) %>% mutate(group='cohort')
)

all_dat %>%
  ggplot(aes(x=year, y=cpkp, color=group)) +
  facet_wrap(~ antibiotic, ncol=3, scales='free_y') +
  geom_point() + geom_line() +
  theme_minimal() +
  ggtitle('Unadjusted consumption, overall or in cohort')
```

This shows a subset of the above data, but using percent changes from 2011 to 2014:

```{r}
all_dat %>%
  arrange(year) %>%
  group_by(group, antibiotic) %>%
  summarize(mean_cpkp=mean(cpkp),
            pct_change=(tail(cpkp, 1)/head(cpkp, 1) - 1)*100) %>%
  ungroup() %>%
  filter(antibiotic %in% top_abx) %>%
  { levels = filter(., group=='cohort') %>% arrange(pct_change) %$% antibiotic;
    mutate(., antibiotic=factor(.$antibiotic, levels=levels)) } %>%
  ggplot(aes(x=antibiotic, y=pct_change, color=group)) +
  geom_point() +
  coord_flip()
```

@@

# Adjusted consumption changes

Only in the cohort:

```{r}
read_tsv('tables/tbl_cohort_model_abx.tsv') %>%
  filter(term=='year', model %in% top_abx) %>%
  arrange(estimate) %>%
  mutate(cpkp_per_year=estimate*1000,
         antibiotic=as_factor(model)) %>%
  select(antibiotic, cpkp_per_year) %>%
  ggplot(aes(x=antibiotic, y=cpkp_per_year)) +
  geom_point() +
  coord_flip() +
  ggtitle('Adjusted changes in consumption') +
  theme_minimal()
```

@@

```{r, eval=FALSE}
condition_names = read_tsv('../chronic-conditions/names.tsv')
